Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

>>>>

Fig. \ref{result_log_1} shows the log obtained from the SI1 case with a value of
significant 0.05. It can be seen that the p-value generated from the test is 0.067. On
the test, the significant value used is 0.05 so that based on
algorithm, in that case it cannot immediately reject h0 and must continue
compare the statistical value with the critical value, and the result
states that the CDF latency in these cases has the same distribution
with the baseline, so that regression is not detected. The same will apply to
all significant values $<0.05$, but in the test with a significant value of 0.1,
SI1 cases will be detected as regression.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch4/log/1-log-new.png}
	\caption{\textit{Log} hasil pengujian kasus SI1 dengan alpha 0,05}
	\label{result_log_1}
\end{figure}
